---
title: "Wallaroo interaction"
author: "Dajun Wang"
site: bookdown::bookdown_site
output:
  pdf_document: default
  bookdown::gitbook: default
  bookdown::pdf_book:
    number_sections: no
  bookdown::pdf_document2:
    number_sections: no
  word_document: default
  html_document:
    df_print: paged
documentclass: book
bibliography: ../../../zot-library.bib
citation_package: none
csl: ../../../cjfas-cite-style.csl
editor_options:
  chunk_output_type: console
spacing: double
always_allow_html: yes
mainfont: Times New Roman
fontsize: 11pt
geometry: margin = 1.2in
lof: yes
lot: yes
header-includes:
- \setlength\parindent{24pt}
- \usepackage{indentfirst}
- \usepackage{setspace}\doublespacing
- \usepackage{lscape}
- \newcommand{\blandscape}{\begin{landscape}}
- \newcommand{\elandscape}{\end{landscape}}
- \usepackage{fancyhdr}
- \pagestyle{plain}
- \fancyfoot[CO, CE]{\thepage}
- \setlength{\headheight}{14.0pt}
- \usepackage{microtype}
- \usepackage{dcolumn}
---

```{r ch4 quick load, include = FALSE}
rm(list = ls())
load("2022-01-18-wallaroo") # 
source("wallaroo_analysis.R") # 
```

```{r setup, include = FALSE}
set.seed(2807)
source("../../../kntr-options-packs.R", local = knitr::knit_global())
Sys.setenv(R_GSCMD="C:/Program Files/gs/gs9.53.3/bin/gswin64.exe")
knitr::opts_chunk$set(fig.pos = 'H') #to set all images to top
options(tinytex.verbose = TRUE)
options(tibble.print_max = Inf) # To show all rows
options(tibble.width = Inf) # To show all columns; Inf controls value

knitr::opts_chunk$set(fig.pos = 'H', fig.width=12, fig.height=8, fig.path='Figs/',echo=FALSE, warning=FALSE, message=FALSE)
```

# Introduction

To explore the change in activity patterns and enclosure space-use in Grey kangaroos with the introduction of Bennet's and Swamp wallabies.

# Methods

# Results


# Discussion

Some key notes to consider; we will need to pair the findings with health parameters from ZIMs report or vets. For instance, 1. Are there any reports of aggression ever since the introduction of the wallabies? 2. Any loss in BCS or increase in stess-related illness?

# References
